\chapter{Data Analysis} \label{cha: data}

\section{Dataset}

\begin{table}[H]
\centering
\begin{tabular}{
|>{\raggedright\arraybackslash}p{0.15\linewidth}
|>{\raggedright\arraybackslash}p{0.13\linewidth}
|>{\raggedright\arraybackslash}p{0.13\linewidth}
|>{\raggedright\arraybackslash}p{0.06\linewidth}
|>{\raggedright\arraybackslash}p{0.07\linewidth}
|>{\raggedright\arraybackslash}p{0.08\linewidth}
|>{\raggedright\arraybackslash}p{0.05\linewidth}
|>{\raggedright\arraybackslash}p{0.12\linewidth}|
}
\hline
\rowcolor[HTML]{D8E9F7} 
\textbf{Dataset} & \textbf{IDs (train/test)} & \textbf{Images total} & \textbf{Train} & \textbf{Query} & \textbf{Gallery} & \textbf{Cam} & \textbf{Annotation} \\ \hline
Market-1501 & 751/750 & 32,668 & 12,936 & 3,368 & 19,732 & 6 & DPM \\ \hline
DukeMTMC-ReID & 702/702  & 36,411 & 16,522 & 2,228 & 17,661 & 8 & Manual \\ \hline
CUHK03 (labeled) & 767/700 & 14,097 & 7,368 & 1,400 & 5,328 & 10 & Manual \\ \hline
CUHK03 (detected) & 767/700 & 14,096 & 7,365 & 1,400 & 5,332 & 10 & DPM \\ \hline
\end{tabular}
\end{table}


\ac{DPM}

\subsection{??Selection criteria}
Open access with a free clear license. Real surveillance conditions. Well defined train, query, and gallery splits. Multiple cameras and resolution variants. Compatibility  with common used \ac{ReID} structure.

\subsection{ReID Dataset}
Market-1501 was collected from The Chinese University of Hong Kong campus setting with 6 non overlapping cameras. Its made for image based \ac{ReID} under realistic variation in in viewpoint, lightning and clothing. Auto detection introduces background noise and compression noise.  which is useful for model robustness. In our experiments we use Market-1501 for baseline \ac{ReID}, sequential \ac{SR} to \ac{ReID}, and for end to end fine tuning.

DukeMTMC-ReID is made from multi camera video setup with 8 cameras and strong outdoor light variation. The dataset has *** Noget om de 408 ekstra billeder der er til for at lave støj så man kan gøre den bedre. ** Preprocessing is simular to Market-1501 **

CUHK03 is smaller 

Licensing and distrubition: We download only from official sources and respect the orginal research licenses for Market-1501 and DukeMTMC-ReID. CUHK03 is used in a non commercial research. 

\subsection{SR Data}

Div2K